Shared Characterizations of Demands and Resources across O*NET Job Elements

### 2025-04-26 Submission.Rmd
pushing apaquarto to Alicia

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands. This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work--related outcomes. We lastly explore the moderating role of resources on these relationships. We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge. Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships. These findings broadly suggest that challenging demands may also be interpreted as job resources, and hindrance demands exhibit considerable variability. These findings have implications for job design and management particularly with regard to demanding elements that may also be experienced as resources.

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job]. The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

@cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

>>>>

abstract: |
  Many discussions of job demands and resources include a tacit characterization that some job elements are resources and others are demands. This study documents variability in ratings of O\*Net job characteristics with respect to subjective interpretation of job characteristics, and further predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes. We additionally explore the potential moderating role of resources on these relationships. The results indicate that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are experienced both as resource and challenge. Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships. These findings broadly suggest that challenging demands may also serve as job resources, and what is viewed as a hindrance exhibits considerable variability. These findings have implications for job design and management particularly with regard to the opportunity with demanding elements: these may be amenable to reframing as resources.

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we investigate these associations retaining [O\*Net specifications](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes. Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

@cavanaugh2000empirical proposed the challenge-hindrance stressor framework that distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

### 2025-04-26 Submission.tex
pushing apaquarto to Alicia

\abstract{%
Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands. This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work--related outcomes. We lastly explore the moderating role of resources on these relationships. We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge. Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships. These findings broadly suggest that challenging demands may also be interpreted as job resources, and hindrance demands exhibit considerable variability. These findings have implications for job design and management particularly with regard to demanding elements that may also be experienced as resources.
}

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

Cavanaugh et al. (2000) proposed the challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity (M. A. LePine, 2022).

>>>>

\abstract{%
Many discussions of job demands and resources include a tacit characterization that some job elements are resources and others are demands. This study documents variability in ratings of O*Net job characteristics with respect to subjective interpretation of job characteristics, and further predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes. We additionally explore the potential moderating role of resources on these relationships. The results indicate that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are experienced both as resource and challenge. Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships. These findings broadly suggest that challenging demands may also serve as job resources, and what is viewed as a hindrance exhibits considerable variability. These findings have implications for job design and management particularly with regard to the opportunity with demanding elements: these may be amenable to reframing as resources.
}

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we investigate these associations retaining \href{https://www.onetcenter.org/content.html}{O*Net specifications}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes. Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

Cavanaugh et al. (2000) proposed the challenge-hindrance stressor framework that distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity (M. A. LePine, 2022).
